\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-07-12 papers/methods/paper.tex
Updating paper

% Abstract of the paper
\begin{abstract}
We present a hierarchical Bayesian model for use in supernova cosmology which takes into account a full range of analysis systematics and selection effects. This advances previous works with hierarchical Bayesian models by including additional sources of systematic uncertainty and improved treatment of Malmquist bias, whilst increasing numerical efficiency. Our model is optimised for efficient fitting and has been validated on a combined simulated dataset of more than $250\,000$ supernovae to rule out the presence of significant model biases in parameter recovery. Simplified statistical simulations for ideal supernovae cosmology show no bias, and sophisticated SNANA simulations of the combined low-redshift and DES 3-year spectroscopic survey sample quantify the bias for flat $w$CDM cosmology, with a matter prior $\Omega_m \sim \mathcal{N}(0.3, 0.01)$ included to allow rigorous determination of model bias in $w$. SNANA simulations can recover the input cosmology to within $0.3\sigma$, while taking into an increased number of systematics than prior analyses.
\end{abstract}
% Bias in SNANA tests across intrinsic dispersion models is found to range from $-0.15\sigma$ to $+0.27\sigma$ in $w$ for datasets of comparable strength to the Dark Energy Survey three-year analysis.

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3\vspace{-5mm}
\end{keywords}

>>>>

% Abstract of the paper
\begin{abstract}
We present a hierarchical Bayesian model for use in supernova cosmology which takes into account a full range of analysis systematics and selection effects. This advances previous works with hierarchical Bayesian models by including additional sources of systematic uncertainty and improved treatment of Malmquist bias, whilst increasing numerical efficiency. Our model is optimised for efficient fitting and has been validated on a combined simulated dataset of more than $250\,000$ supernovae to rule out the presence of significant model biases in parameter recovery. Simplified statistical simulations for ideal supernovae cosmology show no bias, and sophisticated SNANA simulations of the combined low-redshift and DES 3-year spectroscopic survey sample quantify the bias for flat $w$CDM cosmology, with a matter prior $\Omega_m \sim \mathcal{N}(0.3, 0.01)$ included to allow rigorous determination of model bias in $w$. SNANA simulations can recover the input cosmology to within one third of the typical uncertainty for the DES 3-year spectroscopic sample, while taking into an increased number of systematics than prior analyses.
\end{abstract}
% Bias in SNANA tests across intrinsic dispersion models is found to range from $-0.15\sigma$ to $+0.27\sigma$ in $w$ for datasets of comparable strength to the Dark Energy Survey three-year analysis.

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}
